 Response to the referee's comments:

  Let me first thank the referee for giving his comments. Here I am 
addressing all the comments made by the referee.  

1. The first comment is regarding the equation of state in hadron 
phase. It is clear that increasing the degrees of freedom in hadron 
phase will shorten the lifetime of mixed phase and it will induce a 
change in the photon spectrum. I wanted to demonstrate various scenario 
with a three pion gas. But, in the new manuscript I have gone to a 
richer equation of state. I have modified both the figures and the 
numbers according to a rich equation of state described in the text.

2. The second comment about transverse expansion. The transverse 
expansion is important but it has been shown to have very minor effect 
on the photon spectrum at SPS by a number of authors. I am giving this 
in manuscript along with the references [20,21]. Similarly, the baryon 
density effect also has been shown to have only minor effect in the 
photon spectrum at SPS. For this also I am giving reference [22]. 
Knowing that these effects are not going to induce any noticeable 
change at least at SPS I have not introduced these aspects.
 
  I have concentrated mainly on supercooling aspect. I have studied 
how various scenarios of a first order phase transition will manifest 
in the photon spectrum over Idealized Maxwell construction. The main 
conclusions of the manuscript are, supercooling has only marginal 
effect and a sudden hadronization scenario is most improbable. Both 
of these are not going to change by including or not including any 
other aspect.

3. About the comment on initial temperature: the initial conditions 
used have been the most suitable at SPS which I thought need not be 
justified, are now justified in the new manuscript.
[See, the changes in the manuscript.]

  I am sure this study is important and should reach to the heavy ion 
community through publication. With this feeling I request the referee 
to reconsider his decision in light of the changes made in the manuscript.


 Changes in the manuscript:
 
1. In the 5th paragraph after 7 lines I have added justification for 
using particular initial conditions, (1+1) D expansion and baryon free
QGP

2. All the numbers of life time of mixed phase and hadron phase have 
been changed due to change in the eq. of state of hadron phase.
Figure 1 and Fig.2 have been recalculated.

3. I have removed the discussions of the others work in the paragraphs 
before conclusions.

4. The transverse expansion and baryon density discussions in the 
conclusions have been removed as they have already appeared earlier.

5. Refs. [19], [21], [22], [23] have been added. Earlier refs. [23],
[24] and [25] have been removed.


